A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-13 PPSN2016/paper.Rnw
Including and commenting results.
Please @mariosky @fergunet and @unintendedbear take a look at what has been written and comment and so on.

\caption{Ranked and normalized number of contributions (PUTs) per IP,
  plotted in a log $y$ scale.}
\label{fig:zipf}
\end{figure}

@@

Every run had slightly different conditions, although in some cases it
was just a server reboot and a new round of announcements. Each run
batch included at least 30 competions, that is, running until the
solution was found. The number of runs was controlled by polling an
URL that indicated the number of runs made in the present batch so
far. A summary of the experiments and  its results is shown in Table
\ref{tab:runs}. This table shows the median time needed to find the
solution as well as the median number of IPs and PUTs. In this case we
distinguish between the total number of clients participating in that
particular run, and the {\em actual} number whose contributions were
accepted into the cache, which was set up to accept those only if {\em
  new} chromosomes were sent to the server in order to avoid overlaps
between one run and the next. That is why, in both cases, the
``Contributing'' column includes a value that is less than the total
number. The final column includes the total number of runs in that
particular batch, finished after a minimum number of 30 was reached.

@@

So we will have to check whether we have effectively eliminated these
overlaps. In order to do that, we will have to establish a threshold
under which reasonably the solution cannot be found. In every
evolutionary algorithm it might happen, by chance, that the solution
is found in just a few evaluations, but that is usually not the
case. By looking at the logs in the last case we have established that
minimun as 16 PUTs; in less than 1600 generations no solution to that
difficult problem will be found. Let us filter then the runs,
eliminating those that use less than 1600 generations to find the
solution which can reasonably be said that they did so because some
browser ``carried over'' a chromosome from the previous run. The
results are shown in Table \ref{tab:filtered}

>>>>

\caption{Ranked and normalized number of contributions (PUTs) per IP,
  plotted in a log $y$ scale.\label{fig:zipf}}
\label{fig:zipf}
\end{figure}

@@

Every run had slightly different conditions, although in some cases it
was just a server reboot and a new round of announcements. Each run
batch included at least 30 completions, that is, evolution until the
solution was found. The number of runs was controlled by polling an
URL that indicated the number of runs made in the present batch so
far. Every volunteer contributed a certain number of individuals
(represented by the PUT HTTP order) to the server. The ranked number
of contributions per unique IP is shown in Figure \ref{fig:zipf} in a
log-log scale. Besides following the usual Zipf's law found in our
previous work and having a very similar appearance for all 5 sets, it
is interesting to see how some sets have a number of contributions per
IP that is slightly superior to the rest, specially so in {\tt
  graph2}. The last two sets, {\tt reboot} and {\tt cachereboot}, also
show a regime in the middle of the graph that shows that some users
are contributing more than in other similar sets. In general, these
differences in behavior are due more to the specific users that show
up in these experiments than to general laws, but it should also be
noted that those behaviors can be encouraged by design.

A summary of the experiments and  its results is shown in Table
\ref{tab:runs}. This table shows the median time needed to find the
solution as well as the median number of IPs and PUTs. In this case we
distinguish between the total number of clients participating in that
particular run, and the {\em actual} number whose contributions were
accepted into the cache, which was set up to accept those only if {\em
  new} chromosomes were sent to the server in order to avoid overlaps
between one run and the next. That is why, in both cases, the
``Contributing'' column includes a value that is less than the total
number. The final column includes the total number of runs in that
particular batch, finished after a minimum number of 30 was reached.

@@

So we will have to check whether we have effectively eliminated these
overlaps. In order to do that, we will have to establish a threshold
under which reasonably the solution cannot be found. In every
evolutionary algorithm it might happen, by chance, that the solution
is found in just a few evaluations, but that is usually not the
case. By looking at the logs in the last case we have established that
minimun as 16 PUTs; in less than 1600 generations no solution to that
difficult problem will be found. Let us filter then the runs,
eliminating those that use less than 1600 generations to find the
solution which can reasonably be said that they did so because some
browser ``carried over'' a chromosome from the previous run. The
results are shown in Table \ref{tab:filtered}. The first change is in
the column \#Runs, that shows that most of the runs in the initial
configurations found the solution thanks to these carried over
clients. However, in the last two rows, the ones that rebooted clients
when they detected changes in cache, the difference is minimal. This
means that one objective has been reached: if clients reboot when they
detect changes in the cache that imply a new run, overlaps are almost
eliminated.

However, the rest of the measures also changes and so we will refer to
this table from now on.
